mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-17 thesis/thesis.tex
add ETNET2016

\begin{document}
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Bachelor's Thesis}}\\
\vspace{2cm}
%{\Large 題\hspace{8mm}目}\\
%\vspace{1cm}
\underline{\LARGE{mruby Bytecode Loader}} \\
\vspace{0.5cm}
\underline{\Large{Using Bluetooth in Multi-VM Environment}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 15, 2016}\\
\vspace{14mm}
{\Large Division of Systems Science and Applied Informatics,\\Department of Systems Science,\\Schoolo of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}
%\maketitle

>>>>

\begin{document}
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Bachelor's Thesis}}\\
\vspace{2cm}
%{\Large 題\hspace{8mm}目}\\
%\vspace{1cm}
\underline{\LARGE{mruby Bytecode Loader}} \\
\vspace{0.5cm}
\underline{\Large{Using Bluetooth in Multi-VM Environment}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 15, 2016}\\
\vspace{14mm}
{\Large Division of Systems Science and Applied Informatics,\\Department of Systems Science,\\School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}
%\maketitle
